Do return series have power-law tails with the same index?

### 2017-08-02 papers/FX/PaperBody.tex
Revised the introduction section of the thesis. Started programming for the main importance sampling algorithm.
Some minor revision.

\par
Thirdly, Figure~\ref{fig:sectors_parameters} shows that, on
average, the values of $K$
in the ``Energy'' and ``Information Technology'' sectors are  larger
than those in the ``Consumer Staples'' sector.  For a given loss \pro y, 
a larger value of $K$ implies that large losses are more
probable. Thus one can conclude that these two sectors are
considerably riskier than the ``Consumer Staples'' sector. {\red Casper:
we leave this sentence to your discretion.} This is of course a
confirmation of one's economic instinct.

@@

\begin{minipage}{0.5\linewidth}
  \includegraphics[width=\textwidth]{power_utilities.png}
\end{minipage}\hfill
\begin{minipage}{0.42\textwidth}
  The economitrical differences between the two utility functions
  are illustrated in the graph to the left.
  We see that
  $u(x)$ grows slower and saturates later for small $\xi$ than for
  large $\xi$. The latter case represents an agent who is more
  tolerant about low consumption and seeks wealth more
  aggressively. In other words, he is less risk-averse than one with a
  larger $\xi$. Such an agent will therefore invest more heavily in
  equity, as shown in Figure~\ref{fig:phi_hat_pareto}. Note that,
  while $\hat \phi$ changes nearly in the same in both graphs, the
  scales in the graphcs are very different.
\end{minipage}

>>>>

\par
Thirdly, Figure~\ref{fig:sectors_parameters} shows that, on
average, the values of $K$
in the ``Energy'' and ``Information Technology'' sectors are  larger
than those in the ``Consumer Staples'' sector.  For a given loss
probability, a larger value of $K$ implies that large losses are more
probable. Thus one can conclude that these two sectors are
considerably riskier than the ``Consumer Staples'' sector. This is of
course a confirmation of one's economic instinct.

@@

\begin{minipage}{0.5\linewidth}
  \includegraphics[width=\textwidth]{power_utilities.png}
\end{minipage}\hfill
\begin{minipage}{0.42\textwidth}
  The economitrical differences between the two utility functions
  are illustrated in the graph to the left.
  We see that
  $u(x)$ grows slower and saturates later for small $\xi$ than for
  large $\xi$. The latter case represents an agent who is more
  tolerant about low consumption and seeks wealth more
  aggressively. In other words, he is less risk-averse than one with a
  larger $\xi$. Such an agent will therefore invest more heavily in
  equity, as shown in Figure~\ref{fig:phi_hat_pareto}. Note that,
  while $\hat \phi$ changes nearly in the same way in both graphs, the
  scales in the graphcs are very different.
\end{minipage}
